---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# sexscales

<!-- badges: start -->
<!-- badges: end -->

The goal of sexscales is to help you easily calculate (sub)scale scores using the Qualtrics versions of measures in the 4th edition of the *Handbook of Sexuality-Related Measures* (Milhausen et al., 2019). 

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jsakaluk/sexscales")
```
## Example

To use sexscales, you will need to have exported data from a Qualtrics survey (using numeric values) that includes one or more of the pre-programmed measures from *the Handbook*.
Once you have imported the data into a data frame in R, all you need to do is use the appropriate scoring function (e.g., scoreBerglas for Berglas et al.'s Sexual Relationship Rights measure), specify your data frame (e.g., dat), and tell the function the name of the column containing the first variable for the measure in question in the firstq argument (e.g., "AA_SSR_1"). 

```{r example, warning=FALSE, message=FALSE, eval=FALSE}
library(sexscales)

newdat <- scoreBerglas(dat, firstq = "AA_SSR_1")

```
